Verifying Demonstrations

### 2018-11-30 paper/timestamp.tex
Adds that we prefer to share the blockchain with other services

\(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
The \(\TSget\) request returns the hash of the most recent block of the chain (\ie the head).
\footnote{In situations where forks are common, it is relatively easy to adapt this process to look at a few blocks before the head and avoid the issue of the stamp becoming invalid later.}
The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).

Regarding consensus resilience, it is advisable to use a blockchain with a high number of participants even if it means sharing the blockchain with other services.
The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
A similar reasoning can be made with Proof-of-Work consensus in which the computing power of the honest participants must be greater than the one of malicious participants.
In both cases, assuming a majority of honest members in the population, the more participants the merrier.

>>>>

\(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
The \(\TSget\) request returns the hash of the most recent block of the chain 
(\ie the head).%
\footnote{In situations where forks are common, it is relatively easy to adapt this process to look at a few blocks before the head and avoid the issue of the stamp becoming invalid later.}
The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).

Regarding consensus resilience, it is advisable to use a blockchain with a high 
number of participants and preferably sharing the blockchain with other 
services.
The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
A similar reasoning can be made with Proof-of-Work consensus in which the computing power of the honest participants must be greater than the one of malicious participants.
In both cases, assuming a majority of honest members in the population, the more participants the merrier.
We want to share the blockchain with other services due to privacy (and 
anti-censorship) reasons, analogous to the idea of \enquote{domain fronting}.
